### 2023-08-16 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

%%%TITLE, AUTHORS AND ABSTRACT%%%
\twocolumn[
  \begin{@twocolumnfalse}
{\includegraphics[height=30pt]{head_foot/SM}\hfill\raisebox{0pt}[0pt][0pt]{\includegraphics[height=55pt]{head_foot/RSC_LOGO_CMYK}}\\[1ex]
\includegraphics[width=18.5cm]{head_foot/header_bar}}\par
\vspace{1em}
\sffamily
\begin{tabular}{m{4.5cm} p{13.5cm} }
%
\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Hydrodynamics of Multicomponent Vesicles Under Strong Confinement}} \\
\vspace{0.3cm} & \vspace{0.3cm} \\
%
 & \noindent\large{Ashley Gannon,\textit{$^{a}$} Bryan
  Quaife,\textit{${\ast}${$^{a}$}} and Y.-N.
  Young,\textit{${\ast}$$^{b\ddag}$} } \\
% %Author names go here instead of "Full name", etc.
%
\includegraphics{head_foot/dates} & \noindent\normalsize{%We numerically study the hydrodynamics of multicomponent vesicles in two strongly
  %confining geometries.
  We numerically investigate the hydrodynamics and membrane dynamics of multicomponent vesicles in two strongly confined geometries. This serves as a simplified model for red blood
  cells undergoing large deformations while traversing %when passing through extreme
  narrow constrictions. We propose a novel parameterization for the
  bending modulus that remains positive for all lipid phase parameter
  values.	
  %We propose a new bending modulus parameterization that
  %is positive for all values of the lipid phase parameter. 
  For a multicomponent vesicle passing through a stenosis, %we correlate 
  we establish connections between various properties: lipid phase coarsening, size and flow profile of the lubrication layers, %properties (size and flow profile), 
  excess pressure, and the tank-treading velocity of
  the membrane. For a multicomponent vesicle passing through a
  contracting channel, we find that the lipid always phase separates so
  that the vesicle is stiffer in the front as it passes through the
  constriction. %For both cases of confinement we find that the lipid
  %coarsening is arrested under strong confinement, and proceeds with
  %high rate upon relief from extreme confinement. 
  For both cases of confinement, we find that lipid coarsening is
  arrested under strong confinement and proceeds at a high rate upon
  relief from extreme confinement. The results may be useful for
  efficient sorting lipid domains using microfluidic flows by controlled
  release of vesicles passing through strong confinement.} \\
  %The abstrast goes here instead of the text "The abstract should
  %be..."
%
\end{tabular}
%
 \end{@twocolumnfalse} \vspace{0.6cm}
]
%%%END OF TITLE, AUTHORS AND ABSTRACT%%%

@@

%%%MAIN TEXT%%%%
\section{\label{sec:Introduction}Introduction}
Biological membranes, the basic structural units for compartmentalizing
biological systems, 
%have been observed to contain a vast 
exhibit a diverse array of
proteins and lipid species. 
%that phase-separate and form domains or rafts, resulting in spatial
%variations in material properties such as bending stiffness. 
These lipids undergo phase separation, forming domains or rafts that
lead to variations in material properties, including bending stiffness.
Synthetic multicomponent vesicles, self-enclosed lipid bilayer membranes
composed of different lipid species, have been used to study the rich
patterns and accompanying morphologies that emerge from elastic
heterogeneity in the membrane. In a quiescent environment, such elastic
heterogeneity gives rise to wrinkling, budding, adhesion, and fusion of
vesicle membranes~\cite{Lowengrub2009_PRE, Li2012_CommMathSci,
Zhao2011_PRE}, closely related to several cellular
processes~\cite{Rauch2000_BiophysJ, Takeda2003_PNAS}.

@@

The lipid species $u$ is governed by a fourth-order Cahn-Hilliard
equation that results in the lipids phase separating while conserving
their total mass. To model the variable bending,
\citet{soh-tse-li-voi-low2010} parameterized the bending modulus as
\begin{align}
  \label{eqn:linearBending}
  b(u) = (1-u) + \beta u.
\end{align}
However, since the double-well potential does not have hard walls, the
lipid concentration is not guaranteed to be confined to the interval
$[0,1]$. This is problematic since $b(u) < 0$ if $u > (1 - \beta)^{-1}$,
and such values of $u$ are possible when $\beta \ll 1$, $Ca \gg 1$, or
the vesicle is confined to a narrow region. This behavior is
demonstrated in Figure~\ref{fig:concModels}(a) for a vesicle with a
floppy-to-stiff ratio $\beta = 10^{-1}$ entering a stenosis. Using the
linear bending model in Equation~\eqref{eqn:linearBending}, the lipid
concentration achieves a maximum value of $u \approx 1.5$ which results
in an instability that is formed by the resulting unphysical negative
bending stiffness. To rectify this issue, we parameterize the bending
modulus with the sigmoid function
\begin{align}
  b(u) = \frac{\beta-1}{2} \tanh\left(3\left(u-\frac{1}{2} 
    \right)\right) + \frac{\beta + 1}{2}.
  \label{eqn:tanhBending}
\end{align}
This parameterization maps the local minimums of the double-well
potential close to $\beta$ and $1$, but more importantly, b(u) remains
bounded in $(\beta,1)$ even when $u \notin [0,1]$
(Figure~\ref{fig:concModels}(b)). This new bending model is validated in
Section~\ref{sec:validation}.
%To demonstrate the necessity of this new bending model, we consider a
%multicomponent vesicle in strong confinement with both bending
%models~\eqref{eqn:linearBending} and~\eqref{eqn:tanhBending}. The
%stiff-to-floppy ratio is $\beta = 10^{-1}$. In the new
%model~\eqref{eqn:tanhBending}, the lipid concentration achieves a
%maximum value of $u \approx 1.002$ which results in a minimum bending
%stiffness of $b(u) \approx \beta$. However, if we use the linear
%bending model~\eqref{eqn:linearBending}, the lipid concentration
%achieves a maximum value of $u \approx 1.52$ which results in an
%unphysical negative bending stiffness of $b(u) \approx -0.5$. The
%corresponding vesicle shape is in Figure~\ref{fig:concModels}(b), and
%the instability caused by the negative bending stiffness is near the
%region with negative curvature.

\begin{figure}[h]
  \centering
%  \input{figures/concModels.tikz} \\
%  \subfigimg[width=0.9\linewidth, clip ]{(a)}{figures/oldbending.pdf} \\
  \subfigimg[width=0.9\linewidth, clip ]{(a)}{figures/OldBending.pdf} \\
  \subfigimg[width=0.9\linewidth, clip ]{(b)}{figures/concModels.pdf}
  \caption{\label{fig:concModels} \small (a) A multicomponent vesicle
  entering a closely-fitting channel (black lines) using the linear
  model in Equation~\eqref{eqn:linearBending}. An instability is
  introduced where the vesicle bending modulus becomes negative. (b) The
  linear bending model in red (Equation~\eqref{eqn:linearBending}) and
  the new sigmoid bending model in blue
  (Equation~\eqref{eqn:tanhBending}). Note that the new bending model
  satisfies $b \in (\beta,1)$ even if $u \notin [0,1]$.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Validation}
\label{sec:validation}
We validate the new sigmoid bending model in
Equation~\eqref{eqn:tanhBending} by reproducing dynamics reported in the
literature. Figure~\ref{fig:treading} shows a phase treading (top) and a
tank-treading (bottom) multicomponent vesicle in an unconfined linear
shear flow. The simulations align with the results reported
by~\citet{liu-mar-li-vee-low2017} (cf.~Figure 3 and Figure 4).
\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\columnwidth]{figures/shearTreading.pdf}
  \caption{\label{fig:treading} \small A multicomponent vesicle in a
  linear shear flow undergoes phase-treading (top) and tank-treading
  (bottom) with the new sigmoid bending model in
  Equation~\eqref{eqn:tanhBending}. The dimensionless times are in the
  title. The red region is stiff and the blue region is floppy. The
  simulations qualitatively agree with the results presented
  in~\citet{liu-mar-li-vee-low2017}.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:results}Hydrodynamics of a multicomponent vesicle
under strong confinement}
We consider both a single-component and a multicomponent vesicle
suspended in two geometries: a closely-fitting geometry (stenosis) and a
geometry that slowly contracts to a narrow neck and then quickly widens
(contracting). We considered a semipermeable vesicle suspended in these
same geometries in our previous work~\cite{qua-gan-you2021}. All the
multicomponent examples have floppy-to-stiff ratio $\beta = 10^{-1}$.
For the single-component case, we consider two bending stiffnesses:
$b(u) = 1$ and $b(u) = 0.55$. We refer to these cases as a stiff
single-component vesicle and a floppy single-component vesicle,
respectively. The smaller bending stiffness represents the average
bending stiffness of a multicomponent vesicle, when its stiff and floppy
regions cover the same amount of area. Throughout this section we plot
the position of the vesicle in terms of the $x$-coordinate of its center
of mass. For the stenosis geometry in Section~\ref{subsec:Stenosis}, the
narrow region begins at $x=-15$ and ends at $x=15$. For the contracting
geometry in Section~\ref{subsec:Contraction}, the geometry begins to
narrow at $x=4$ and reaches its narrowest point at $x=15$.

@@

Another difference between the two reduced areas is that the vesicles
with smaller reduced area undergo tank-treading motions. As mentioned
earlier, tank-treading occurs when the top and bottom lubrication layers
differ in size. The size of the lubrication layers for all three cases
of the vesicle with reduced area $\alpha = 0.4$ are in the top half of
Figure~\ref{fig:lubricationComposite}. The bottom of
Figure~\ref{fig:lubricationComposite} shows the tank-treading velocities
of four Lagrangian points. The inset shows the vesicle configuration in
the closely-fitting part of the channel, the black dashed line is the
center line of the channel, the marks are the four Lagrangian points,
and the rounded arrow denotes the direction of rotation. The stiff
single-component and multicomponent vesicles are clearly tank treading.
The direction and speed of the tank-treading depends on the how much of
the vesicle membrane is exposed to positive shear (below the center
line) versus how much is exposed to negative shear (above the center
line). The majority of the membrane of the stiff single-component and
multicomponent vesicles are below the center line, and this results in a
clockwise tank-treading behavior. In contrast, the majority of the
membrane of the floppy single-component vesicle is above the center
line, and the result is counterclockwise tank-treading. In addition, the
tank-treading velocity can be correlated to the percentage of its
membrane that is below the center line. We note, however, that the
floppy single-component vesicle is still undergoing deformations, so the
tangential velocities have not converged to a fixed value.

@@

When a vesicle is tank-treading near a solid wall, the flow in the thin
layer of fluid includes both a linear profile and a Poiseuille
profile~\cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}.
The magnitude of the Poiseuille profile is determined by the pressure
gradient between the vesicle and the solid wall, while the linear
profile is determined by the tangential velocity of the vesicle relative
to the solid wall. Using the definition of the lubrication layer
outlined in Section~\ref{sec:LL}, we consider the flow profile inside
this lubrication layer in Figure~\ref{fig:BLvelocities}. We observe that
the Poiseuille coefficient (quadratic term) can be either positive or
negative, meaning that the pressure gradient in the streamwise direction
in the lubrication layer switches signs. The Poiseuille coefficient is
related to the lateral gradient of the tangential traction,
$\mathbf{F}_\tt$, on the vesicle membrane~\cite{Oron1997_RMP,
Young2014_JFM}
\begin{align}
  \mathbf{F}_{\tt} = -\sigma_s + u_s \frac{\delta E^m}{\delta u}.
\end{align}
Here,
\begin{align}
  \frac{\delta E^m}{\delta u} = \frac{a}{\epsilon} 
    (f'(u) - \epsilon^2 u_{ss}) + \frac{b'(u)}{2} \kappa^2
\end{align}
is the derivative of the membrane energy with respect to the lipid
concentration~\cite{soh-tse-li-voi-low2010}. Note that in the
single-component case, the tangential traction is $\mathbf{F}_\tt =
-\sigma_s$ which is the usual Marangoni effect.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{subsec:Contraction} A multicomponent vesicle in the
contracting geometry}
In this section, we consider a vesicle passing through a geometry that
slowly contracts to a region that is only 2~$\mu$m wide, and then
immediately opens back up to a channel that is ten times larger. We
first consider the effect of the initial lipid concentration when the
floppy and stiff regions each make up half of the vesicle membrane. In
Figure~\ref{fig:RA6leftRightRand}, snapshots of vesicles with reduced
area $\alpha = 0.5$ with different initial lipid distributions are
illustrated. The initial distributions are (a) random, (b) stiff in the
front and floppy in the back, and (c) floppy in the front and stiff in
the back. The vesicle with the random initial lipid distribution quickly
phase separates into two floppy and two stiff regions. As seen in the
stenosis geometry, further phase separation is delayed until the vesicle
is no longer under strong confinement. The vesicle with the stiff region
at the front maintains its orientation. In contrast, the vesicle with
the floppy region on the front reorients the floppy region towards the
back of the vesicle. In summary, in all three cases, the vesicle is
orienting itself so that the stiff region passes through the
constriction before the floppy region. Therefore, in subsequent
simulations, we initialize the vesicle's lipid concentration so that the
floppy region is in the back and its stiff region is in the front. The
vesicle shapes develop regions with high curvature in the floppy region
when they first pass through the narrowest part of the geometry, but
once the strong confinement is abruptly removed, these regions of high
curvature are quickly smoothed.

@@

\begin{table}[h]
  \centering
  \begin{tabular}{l|ccccc}
    \hline
    Floppy percentage & 0\% & 15\% & 25\% & 35\% & 45\% \\ 
    Time  & 2.32 & 2.30 & 2.29 & 2.26 & 2.24 \\
    \hline
  \end{tabular}
  \caption{\label{tbl:contractingTimes} \small The time required for the
  vesicles to completely pass through the neck.}
\end{table}

@@

resources: BQ, YNY; data curation: AG, BQ, YNY; writing - original

@@

visualization: AG, BQ; supervision: BQ, YNY; project administration: BQ,

@@

\section*{Acknowledgements}
We thank David Salac and Shuwang Li for discussions. B.Q.~acknowledges
support from the Simons Foundation, Mathematics and Physical
Sciences-Collaboration Grants for Mathematicians, Award No.~527139.
Y.-N.Y.~acknowledges support from NSF (Grants No.~DMS 1614863 and
No.~DMS 195160) and Flatiron Institute, part of Simons Foundation.
%The Acknowledgements come at the end of an article after Conflicts of interest and before the Notes and references.

>>>>

%%%TITLE, AUTHORS AND ABSTRACT%%%
\twocolumn[
  \begin{@twocolumnfalse}
{\includegraphics[height=30pt]{head_foot/SM}\hfill\raisebox{0pt}[0pt][0pt]{\includegraphics[height=55pt]{head_foot/RSC_LOGO_CMYK}}\\[1ex]
\includegraphics[width=18.5cm]{head_foot/header_bar}}\par
\vspace{1em}
\sffamily
\begin{tabular}{m{4.5cm} p{13.5cm} }
%
\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Hydrodynamics of Multicomponent Vesicles Under Strong Confinement}} \\
\vspace{0.3cm} & \vspace{0.3cm} \\
%
 & \noindent\large{Ashley Gannon,\textit{$^{a}$} Bryan
  Quaife,\textit{${\ast}${$^{a}$}} and Y.-N.
  Young,\textit{${\ast}$$^{b\ddag}$} } \\
% %Author names go here instead of "Full name", etc.
%
\includegraphics{head_foot/dates} & \noindent\normalsize{%We numerically study the hydrodynamics of multicomponent vesicles in two strongly
  %confining geometries.
  We numerically investigate the hydrodynamics and membrane dynamics of multicomponent vesicles in two strongly confined geometries. This serves as a simplified model for red blood
  cells undergoing large deformations while traversing %when passing through extreme
  narrow constrictions. We propose a new parameterization for the
  bending modulus that remains positive for all lipid phase parameter
  values.	
  %We propose a new bending modulus parameterization that
  %is positive for all values of the lipid phase parameter. 
  For a multicomponent vesicle passing through a stenosis, %we correlate 
  we establish connections between various properties: lipid phase coarsening, size and flow profile of the lubrication layers, %properties (size and flow profile), 
  excess pressure, and the tank-treading velocity of
  the membrane. For a multicomponent vesicle passing through a
  contracting channel, we find that the lipid always phase separates so
  that the vesicle is stiffer in the front as it passes through the
  constriction. %For both cases of confinement we find that the lipid
  %coarsening is arrested under strong confinement, and proceeds with
  %high rate upon relief from extreme confinement. 
  For both cases of confinement, we find that lipid coarsening is
  arrested under strong confinement and proceeds at a high rate upon
  relief from extreme confinement. The results may be useful for
  efficient sorting lipid domains using microfluidic flows by controlled
  release of vesicles passing through strong confinement.} \\
  %The abstrast goes here instead of the text "The abstract should
  %be..."
%
\end{tabular}
%
 \end{@twocolumnfalse} \vspace{0.6cm}
]
%%%END OF TITLE, AUTHORS AND ABSTRACT%%%

@@

%%%MAIN TEXT%%%%
\section{\label{sec:Introduction}Introduction}
Biological membranes, the basic structural units for compartmentalizing
biological systems, 
%have been observed to contain a vast 
comprise diverse arrays of
%exhibit a diverse array of
proteins and lipid species. 
%that phase-separate and form domains or rafts, resulting in spatial
%variations in material properties such as bending stiffness. 
These lipids undergo phase separation, forming domains or rafts that
lead to variations in material properties, including bending stiffness.
Synthetic multicomponent vesicles, self-enclosed lipid bilayer membranes
composed of different lipid species, have been used to study the rich
patterns and accompanying morphologies that emerge from elastic
heterogeneity in the membrane. In a quiescent environment, such elastic
heterogeneity gives rise to wrinkling, budding, adhesion, and fusion of
vesicle membranes~\cite{Lowengrub2009_PRE, Li2012_CommMathSci,
Zhao2011_PRE}, closely related to several cellular
processes~\cite{Rauch2000_BiophysJ, Takeda2003_PNAS}.

@@

The lipid species $u$ is governed by a fourth-order Cahn-Hilliard
equation that results in the lipids phase separating while conserving
their total mass. To model the variable bending,
\citet{soh-tse-li-voi-low2010} parameterized the bending modulus as
\begin{align}
  \label{eqn:linearBending}
  b(u) = (1-u) + \beta u.
\end{align}
However, since the double-well potential does not have hard walls, the
lipid concentration is not guaranteed to be confined to the interval
$[0,1]$. This is problematic since $b(u) < 0$ if $u > (1 - \beta)^{-1}$,
and such values of $u$ are possible when $\beta \ll 1$, $Ca \gg 1$, or
the vesicle is confined to a narrow region. This behavior is
demonstrated in Figure~\ref{fig:concModels}(a) for a vesicle with a
floppy-to-stiff ratio $\beta = 10^{-1}$ entering a stenosis. Using the
linear bending model in Equation~\eqref{eqn:linearBending}, the lipid
concentration achieves a maximum value of $u \approx 1.5$ which results
in an instability that is formed by the resulting unphysical negative
bending stiffness. To rectify this issue, we parameterize the bending
modulus with the sigmoid function
\begin{align}
  b(u) = \frac{\beta-1}{2} \tanh\left(3\left(u-\frac{1}{2} 
    \right)\right) + \frac{\beta + 1}{2}.
  \label{eqn:tanhBending}
\end{align}
This parameterization maps the local minimums of the double-well
potential close to $\beta$ and $1$, but more importantly, $b(u)$ remains
bounded in $(\beta,1)$ even when $u \notin [0,1]$
(Figure~\ref{fig:concModels}(b)). We compare this new bending model against the linear model for 
a phase-treading and tank treading vesicle in Section~\ref{sec:validation}.

%To demonstrate the necessity of this new bending model, we consider a
%multicomponent vesicle in strong confinement with both bending
%models~\eqref{eqn:linearBending} and~\eqref{eqn:tanhBending}. The
%stiff-to-floppy ratio is $\beta = 10^{-1}$. In the new
%model~\eqref{eqn:tanhBending}, the lipid concentration achieves a
%maximum value of $u \approx 1.002$ which results in a minimum bending
%stiffness of $b(u) \approx \beta$. However, if we use the linear
%bending model~\eqref{eqn:linearBending}, the lipid concentration
%achieves a maximum value of $u \approx 1.52$ which results in an
%unphysical negative bending stiffness of $b(u) \approx -0.5$. The
%corresponding vesicle shape is in Figure~\ref{fig:concModels}(b), and
%the instability caused by the negative bending stiffness is near the
%region with negative curvature.

\begin{figure}[h]
  \centering
%  \input{figures/concModels.tikz} \\
%  \subfigimg[width=0.9\linewidth, clip ]{(a)}{figures/oldbending.pdf} \\
  \subfigimg[width=0.9\linewidth, clip ]{(a)}{figures/OldBending.pdf} \\
  \subfigimg[width=0.9\linewidth, clip ]{(b)}{figures/concModels.pdf}
  \caption{\label{fig:concModels} \small (a) A multicomponent vesicle
  entering a closely-fitting channel (black lines) using the linear
  model in Equation~\eqref{eqn:linearBending}.  The color denotes the bending modulus $b(u)$.
  An instability is
  introduced where the vesicle bending modulus becomes negative. (b) The
  linear bending model in red (Equation~\eqref{eqn:linearBending}) and
  the new sigmoid bending model in blue
  (Equation~\eqref{eqn:tanhBending}). Note that the new bending model
  satisfies $b \in (\beta,1)$ even if $u \notin [0,1]$.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Validation}
\label{sec:validation}
We validate the new sigmoid bending model in
Equation~\eqref{eqn:tanhBending} by reproducing dynamics reported in the
literature. Figure~\ref{fig:treading} shows a phase treading (top) and a
tank-treading (bottom) multicomponent vesicle in an unconfined linear
shear flow. The simulations align with the results reported
by~\citet{liu-mar-li-vee-low2017} (cf.~Figure 3 and Figure 4).
\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\columnwidth]{figures/shearTreading.pdf}
  \caption{\label{fig:treading} \small A multicomponent vesicle in a
  linear shear flow undergoes phase-treading (top) and tank-treading
  (bottom) with the new sigmoid bending model in
  Equation~\eqref{eqn:tanhBending}. The dimensionless times are in the
  title. The red region is stiff and the blue region is floppy. The
  simulations agree with the results
  in~\citet{liu-mar-li-vee-low2017}.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:results}Hydrodynamics of a multicomponent vesicle
under strong confinement}
We consider both a single-component and a multicomponent vesicle
suspended in two geometries: a closely-fitting geometry (stenosis) and a
geometry that slowly contracts to a narrow neck and then quickly widens
(contracting). 
%We considered a semipermeable vesicle suspended in these
%same geometries in our previous work~\cite{qua-gan-you2021}. 
All the multicomponent examples have floppy-to-stiff ratio $\beta = 10^{-1}$.
For the single-component case, we consider two bending stiffnesses:
$b(u) = 1$ and $b(u) = 0.55$. We refer to these cases as a stiff
single-component vesicle and a floppy single-component vesicle,
respectively. The smaller bending stiffness represents the average
bending stiffness of a multicomponent vesicle, when its stiff and floppy
regions cover the same amount of area. Throughout this section we plot
the position of the vesicle in terms of the $x$-coordinate of its center
of mass. For the stenosis geometry in Section~\ref{subsec:Stenosis}, the
narrow region begins at $x=-15$ and ends at $x=15$. For the contracting
geometry in Section~\ref{subsec:Contraction}, the geometry begins to
narrow at $x=4$ and reaches its narrowest point at $x=15$.

@@

Another difference between the two reduced areas is that the vesicles
with smaller reduced area undergo tank-treading motions. As mentioned
earlier, tank-treading occurs when the top and bottom lubrication layers
differ in size. The size of the lubrication layers for all three cases
of the vesicle with reduced area $\alpha = 0.4$ are in the top half of
Figure~\ref{fig:lubricationComposite}. The bottom of
Figure~\ref{fig:lubricationComposite} shows the tank-treading velocities
of four Lagrangian points. The inset shows the vesicle configuration in
the closely-fitting part of the channel, the black dashed line is the
center line of the channel, the marks are the four Lagrangian points,
and the rounded arrow denotes the direction of rotation. The stiff
single-component and multicomponent vesicles are clearly tank treading.
The direction and speed of the tank-treading depends on how much of
the vesicle membrane is exposed to positive shear (below the center
line) versus how much is exposed to negative shear (above the center
line) \cite{kao-bir-mis2009}. The majority of the membrane of the stiff single-component and
multicomponent vesicles are below the center line, and this results in a
clockwise tank-treading behavior. In contrast, the majority of the
membrane of the floppy single-component vesicle is above the center
line, and the result is counterclockwise tank-treading. In addition, the
tank-treading velocity can be correlated to the percentage of its
membrane that is below the center line. We note, however, that the
floppy single-component vesicle is still undergoing deformations, so the
tangential velocities have not converged to a fixed value.

@@

When a vesicle is tank-treading near a solid wall, the flow in the thin
layer of fluid includes both a linear profile and a Poiseuille
profile~\cite{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}.
The magnitude of the Poiseuille profile is determined by the pressure
gradient between the vesicle and the solid wall, while the linear
profile is determined by the tangential velocity of the vesicle relative
to the solid wall. Using the definition of the lubrication layer
outlined in Section~\ref{sec:LL}, we consider the flow profile inside
this lubrication layer in Figure~\ref{fig:BLvelocities}. We observe that
the Poiseuille coefficient (quadratic term) can be either positive or
negative, meaning that the pressure gradient in the streamwise direction
in the lubrication layer switches signs. The Poiseuille coefficient is
related to the lateral gradient of the tangential traction,
$\mathbf{F}_\tt$, on the vesicle membrane~\cite{Oron1997_RMP,
Young2014_JFM}
\begin{align}
  \mathbf{F}_{\tt} = -\sigma_s + u_s \frac{\delta E^m}{\delta u}.
\end{align}
Here,
\begin{align}
  \frac{\delta E^m}{\delta u} = \frac{a}{\epsilon} 
    (f'(u) - \epsilon^2 u_{ss}) + \frac{b'(u)}{2} \kappa^2
\end{align}
is the derivative of the membrane energy with respect to the lipid
concentration~\cite{soh-tse-li-voi-low2010}. Note that in the
single-component case, the tangential traction is $\mathbf{F}_\tt =
-\sigma_s$ which is the Marangoni stress.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{subsec:Contraction} A multicomponent vesicle in the
contracting geometry}
In this section, we consider a vesicle passing through a channel that
slowly contracts to a  2~$\mu$m wide neck, and then
immediately opens up to a channel that is ten times larger. We
first consider the effect of the initial lipid concentration when the
floppy and stiff regions each make up half of the vesicle membrane. In
Figure~\ref{fig:RA6leftRightRand}, snapshots of vesicles with reduced
area $\alpha = 0.5$ with different initial lipid distributions are
illustrated. The initial distributions are (a) random, (b) stiff in the
front and floppy in the back, and (c) floppy in the front and stiff in
the back. The vesicle with the random initial lipid distribution quickly
phase separates into two floppy and two stiff regions. As seen in the
stenosis geometry, further phase separation is delayed until the vesicle
is no longer under strong confinement. The vesicle with the stiff region
at the front maintains its orientation. In contrast, the vesicle with
the floppy region on the front reorients the floppy region towards the
back of the vesicle. In summary, in all three cases, the vesicle is
orienting itself so that the stiff region passes through the
constriction before the floppy region. Therefore, in subsequent
simulations, we initialize the vesicle's lipid concentration so that the
floppy region is in the back and its stiff region is in the front. The
vesicle shapes develop regions with high curvature in the floppy region
when they first pass through the narrowest part of the geometry, but
once the strong confinement is abruptly removed, these regions of high
curvature are quickly smoothed.

@@

\begin{table}[h]
  \centering
  \begin{tabular}{l|ccccc}
    \hline
    Floppy percentage & 0\% & 15\% & 25\% & 35\% & 45\% \\ 
    Time  (dimensionless) & 2.32 & 2.30 & 2.29 & 2.26 & 2.24 \\
    \hline
  \end{tabular}
  \caption{\label{tbl:contractingTimes} \small The time required for the
  vesicles to completely pass through the neck.}
\end{table}

@@

data curation: AG, BQ, YNY; writing - original

@@

visualization: AG, BQ, YNY; supervision: BQ, YNY; project administration: BQ,

@@

\section*{Acknowledgements}
We thank David Salac  for discussions, and Shuwang Li for discussions and sharing his code for a multicomponent vesicle in free space. 
B.Q.~acknowledges support from the Simons Foundation, Mathematics and Physical
Sciences-Collaboration Grants for Mathematicians, Award No.~527139.
Y.-N.Y.~acknowledges support from NSF (Grants No.~DMS 1614863 and
No.~DMS 195160) and Flatiron Institute, part of Simons Foundation.
%The Acknowledgements come at the end of an article after Conflicts of interest and before the Notes and references.
